### 2018-08-17 introduction.tex
Resolved issue #8 . Number and depletion code removed from Table 1. Numbers in text substituted with references

\section{Introduction}
% State the objectives of the work and provide an adequate background, avoiding
% a detailed literature survey or a summary of the results.
The \gls{MSR} is an advanced nuclear reactor developed at \gls{ORNL} 
in the 1950s and operated in the 1960s. More recently, the \gls{GIF} included 
\glspl{MSR} amon the six advanced reactor concepts promising for further 
research and development.
\glspl{MSR} offer significant improvements ``in the four broad areas of 
sustainability, economics, safety and reliability, and proliferation resistance 
and physical protection" \cite{doe_technology_2002}. To achieve the goals 
formulated by the GIF, \glspl{MSR} attempt to simplify the reactor core and 
improve inherent safety by using liquid fuel.

 In the thermal spectrum \gls{MSR}, fluorides of fissile and/or fertile 
 materials (i.e. UF$_4$, ThF$_4$,  PuF$_3$, TRU\footnote{ Transuranic 
 elements}F$_3$) combine with carrier salts to form a liquid fuel that 
 circulates in a loop-type primary circuit \cite{haubenreich_experience_1970}.  
 Immediate advantages over traditional, solid-fueled, reactors include 
 near-atmospheric pressure in the primary loop, 
 relatively high coolant temperature, outstanding neutron economy, improved 
 safety parameters, reduced fuel preprocessing, and the ability to 
 continuously remove fission products and add fissile and/or fertile elements 
 \cite{leblanc_molten_2010}. The thorium-fueled \gls{MSBR} was developed in the 
 early 1970s by \gls{ORNL} to explore the promise of the thorium 
 fuel cycle, which uses natural thorium instead of enriched uranium. With 
 continuous fuel reprocessing, the \gls{MSBR}
 realizes the advantages of the thorium fuel cycle because the $^{233}$U bred from 
 $^{232}$Th is almost instantly \footnote{\space $^{232}$Th transmutes into 
 $^{233}$Th after capturing a neutron. Next, this isotope decays to $^{233}$Pa 
 ($\tau_{1/2}$=21.83m), which finally decays to $^{233}$U 
 ($\tau_{1/2}$=26.967d).} recycled back to the core 
 \cite{betzler_modeling_2016}. The chosen fuel salt, 
 LiF-BeF$_2$-ThF$_4$-UF$_4$, has a $499^\circ$C melting point, a low vapor 
 pressure at operating temperatures, 
 and good flow and heat transfer properties \cite{robertson_conceptual_1971}. 
 In the matter of nuclear fuel cycle, the thorium cycle produces a reduced 
 quantity of plutonium and \glspl{MA} compared to the traditional uranium fuel 
 cycle. Finally, the \gls{MSR} also could be employed as a converter reactor 
 for transmutation of spent fuel from current \glspl{LWR}.

Liquid-fueled systems present a challenge to existing neutron transport and 
depletion tools which are typically designed to simulate solid-fueled reactors.  
To handle the material flows and potential online removal and feed of 
liquid-fueled systems, early \gls{MSR} simulation methods at \gls{ORNL} 
integrated neutronics and fuel cycle codes (i.e., \gls{ROD} 
\cite{bauman_rod:_1971}) into operational plant tools (i.e., \gls{MRPP} 
\cite{kee_mrpp:_1976}) for \gls{MSR} and reprocessing system design.  Based on 
this approach, recent tools from universities and research institutions can 
approximate online refueling \cite{serp_molten_2014}.  Recent research efforts 
in Europe and Asia mainly focus on fast spectrum reactor fuel cycle analysis. 
These  couple external tools to neutron transport while depletion codes take into 
account continuous feeds and removals in \glspl{MSR}. A summary of recent 
efforts are listed in table~\ref{tab:fs_codes}.

\begin{table}[ht!]
\caption{Tools and methods for fast spectrum system fuel cycle analysis.}
\begin{tabularx}{\textwidth}{ x | s | s | m | x } \hline & Neutronic code  & 
Depletion code    & \qquad Authors & Spectra   \\
\hline
1 & \gls{MCNP} \cite{noauthor_mcnp_2004}      & REM 
\cite{heuer_simulation_2010}  & Doligez \emph{et al.}, 2014; Heuer \emph{et 
al.}, 2014  \cite{doligez_coupled_2014,heuer_towards_2014}    & fast \\
\hline
2 & ERANOS \cite{ruggieri_eranos_2006}      & ERANOS     & Fiorina \emph{et 
al.}, 2013 \cite{fiorina_investigation_2013}            & fast \\
\hline
3 & KENO-IV \cite{goluoglu_monte_2011}     & ORIGEN \cite{gauld_isotopic_2011}     
& Sheu \emph{et al.}, 2013 \cite{sheu_depletion_2013} & fast \\
\hline
4 & SERPENT 2 \cite{leppanen_serpent_2015-1}   & SERPENT 2  & Aufiero \emph{et 
al.}, 2013 \cite{aufiero_extended_2013} & fast \\
\hline
5 & MCODE \cite{xu_mcode_2008}      & ORIGEN2 \cite{croff_users_1980}      & 
Ahmad \emph{et al.}, 2015 \cite{ahmad_neutronics_2015}   & thermal  \\
\hline
6 & \gls{MCNP}6     & CINDER90 \cite{goorley_mcnp6_2013}     & Park \emph{et 
al.}, 2015; Jeong \emph{et al.}, 2016 \cite{park_whole_2015, 
jeong_equilibrium_2016}& thermal\\
\hline
7 & SCALE \cite{bowman_scale_2011}      & SCALE/ ChemTriton 
\cite{powers_new_2013}    & Powers \emph{et al.}, 2014; Betzler \emph{et al.}, 
2017 \cite{powers_new_2013,powers_inventory_2014,betzler_molten_2017}& 
thermal\\
\hline
8 & SERPENT 2      & SERPENT 2     & Rykhlevskii \emph{et al.}, 2017 
\cite{rykhlevskii_online_2017} & thermal\\
\hline
9 & \gls{MCNP}      & REM  & Nuttin \emph{et al.} 
\cite{nuttin_potential_2005}&thermal  \\ \hline
\end{tabularx}
  \label{tab:fs_codes}
\end{table}
\FloatBarrier

@@

Methods (1, 3, 4) provide some form of reactivity control, and methods (1, 4, 
5, 6, 8, 9) use a set of all nuclides in depletion calculations.

Liquid-fueled \gls{MSR} designs have online separations and/or feeds, where 
material is moved to or from the core at all times (continuous) or at specific 
time steps (batch). To account for batch discharge, a depletion tool must 
remove some or all material at specified intervals. This requires the burn-up 
simulation to stop at a given time and restart with a new liquid fuel 
composition (after removal of discarded materials and addition of 
fissile/fertile materials). Accounting for a continuous removal or addition is 
more difficult because it requires adding a term to the Bateman equations. In 
SCALE \cite{bowman_scale_2011}, ORIGEN \cite{gauld_isotopic_2011} solves a set 
of Bateman equations using spectrum-averaged fluxes and cross sections 
generated from a deterministic transport calculation. Methods (1, 4, 8) model 
true continuous feeds and removals, while other methods employ a batch-wise 
approach. \gls{ORNL} researchers have developed ChemTriton, a Python-based 
script for SCALE/TRITON which uses a semi-continuous batch process to simulate 
a continuous reprocessing. This tool models salt treatment, separations, 
discharge, and refill using a unit-cell \gls{MSR} SCALE/TRITON model over small 
time steps to simulate continuous reprocessing and deplete the fuel salt 
\cite{powers_new_2013}.

Thorium-fueled \gls{MSBR}-like reactors similar to the one in this work are 
described in (6, 7, 8, 9). Nevertheless, most of these efforts considered only 
simplified unit-cell geometry because depletion computations for a many-year 
fuel cycle are computationally expesive even for simple models.

>>>>

\section{Introduction}
% State the objectives of the work and provide an adequate background, avoiding
% a detailed literature survey or a summary of the results.
The \gls{MSR} is an advanced type of reactor which was developed at \gls{ORNL} in the 1950s and was operated in the 1960s. More recently, \gls{MSR} was included in the six advanced reactor concepts that have been chosen by the Generation IV International Forum (GIF) for further research and development. \glspl{MSR} offer significant improvements ``in the four broad areas of sustainability, economics, safety and reliability, and proliferation resistance and physical protection" \cite{doe_technology_2002}. To achieve the goals formulated by the GIF, \glspl{MSR} attempt to simplify the reactor core and improve inherent safety by using liquid coolant which is also a fuel.

 In the thermal spectrum \gls{MSR}, fluorides of fissile and/or fertile materials (i.e. UF$_4$, ThF$_4$,  PuF$_3$, TRU\footnote{ Transuranic elements}F$_3$) are mixed with carrier salts to form a liquid fuel which is circulated in a loop-type primary circuit \cite{haubenreich_experience_1970}. This innovation leads to immediate advantages over traditional, solid-fueled, reactors. These include near-atmospheric pressure in the primary loop, relatively high coolant temperature, outstanding neutron economy, a high level of inherent safety, reduced fuel preprocessing, and the ability to continuously remove fission products and add fissile and/or fertile elements \cite{leblanc_molten_2010}. The thorium-fueled \gls{MSBR} was developed in the early 1970s by \gls{ORNL} specifically to realize the promise of the thorium fuel cycle, which uses natural thorium instead of enriched uranium. With continuous fuel reprocessing, \gls{MSBR} is very attractive to effecively realize advantages of the thorium fuel cycle because the $^{233}$U bred from $^{232}$Th is almost instantly \footnote{\space $^{232}$Th transmutes into $^{233}$Th after capturing a neutron. Next, this isotope decays to $^{233}$Pa ($\tau_{1/2}$=21.83m), which finally decays to $^{233}$U ($\tau_{1/2}$=26.967d).} being recycled back to the core \cite{betzler_modeling_2016}. The mixture of LiF-BeF$_2$-ThF$_4$-UF$_4$ has a melting point of $499^\circ$C, a low vapor pressure at operating temperatures, and good flow and heat transfer properties \cite{robertson_conceptual_1971}. In the matter of nuclear fuel cycle, the thorium cycle produces a reduced quantity of plutonium and \glspl{MA} compared to the traditional uranium fuel cycle. Finally, the \gls{MSR} also could be employed as a converter reactor for transmutation of spent fuel from current \glspl{LWR}.

Modeling liquid-fueled systems with existing neutron transport and depletion tools is challenging because most of these tools are designed for the solid-fueled reactors simulation. The fuel material flows and potential online separations or feeds of specific elements or nuclides are the main challenges
of liquid-fueled systems. Furthermore, no established tool for liquid-fueled \gls{MSR} neutronics and fuel cycle evaluation exist, though internally developed tools from universities and research institutions can approximate online refueling \cite{serp_molten_2014}. The foundation for these tools was based on early \gls{MSR} simulation methods at \gls{ORNL}, which integrated neutronics and fuel cycle codes (i.e., ROD \cite{bauman_rod:_1971}) into operational plant tools (i.e., MRPP \cite{kee_mrpp:_1976}) for \gls{MSR} and reprocessing system design. More recent research efforts in Europe and Asia mainly focus on fast spectrum reactor fuel cycle analysis and couple external tools to neutron transport and depletion codes take into account continuous feeds and removals in \glspl{MSR}. Four of these efforts are listed in table~\ref{tab:fs_codes}.

\begin{table}[ht!]
\caption{Tools and methods for fast spectrum system fuel cycle analysis.}
\begin{tabularx}{\textwidth}{ m | b | x } 
\hline Neutronic code    & \qquad Authors & Spectra   \\
\hline
\gls{MCNP}/REM \cite{noauthor_mcnp_2004,heuer_simulation_2010}  & Doligez \emph{et al.}, 2014; Heuer \emph{et al.}, 2014  \cite{doligez_coupled_2014,heuer_towards_2014}    & fast \\
\hline
ERANOS \cite{ruggieri_eranos_2006}  & Fiorina \emph{et al.}, 2013 \cite{fiorina_investigation_2013}            & fast \\
\hline
KENO-IV/ORIGEN \cite{goluoglu_monte_2011,gauld_isotopic_2011}     & Sheu \emph{et al.}, 2013 \cite{sheu_depletion_2013} & fast \\
\hline
SERPENT 2 \cite{leppanen_serpent_2015-1}  & Aufiero \emph{et al.}, 2013 \cite{aufiero_extended_2013} & fast \\
\hline
MCODE/ORIGEN2 \cite{xu_mcode_2008,croff_users_1980}      & Ahmad \emph{et al.}, 2015 \cite{ahmad_neutronics_2015}   & thermal  \\
\hline
\gls{MCNP}6/CINDER90 \cite{goorley_mcnp6_2013}     & Park \emph{et al.}, 2015; Jeong \emph{et al.}, 2016 \cite{park_whole_2015, jeong_equilibrium_2016}& thermal\\
\hline
SCALE/TRITON \cite{bowman_scale_2011,powers_new_2013}    & Powers \emph{et al.}, 2014; Betzler \emph{et al.}, 2017 \cite{powers_new_2013,powers_inventory_2014,betzler_molten_2017}& thermal\\
\hline
SERPENT 2     & Rykhlevskii \emph{et al.}, 2017 \cite{rykhlevskii_online_2017} & thermal\\
\hline
\gls{MCNP}/REM  & Nuttin \emph{et al.} \cite{nuttin_potential_2005}&thermal  \\ \hline
\end{tabularx}
  \label{tab:fs_codes}
\end{table}
\FloatBarrier

@@

References \cite{doligez_coupled_2014,heuer_towards_2014,sheu_depletion_2013,aufiero_extended_2013} provide some form of reactivity control, and methods \cite{doligez_coupled_2014,heuer_towards_2014,aufiero_extended_2013,ahmad_neutronics_2015, park_whole_2015, jeong_equilibrium_2016,rykhlevskii_online_2017,nuttin_potential_2005} use a set of all nuclides in depletion calculations.

Liquid-fueled \gls{MSR} designs have online separations and/or feeds, where material is moved to or from the core at all times (continuous) or at specific time steps (batch). To account for batch discharge, a depletion tool must remove some or all material at specified intervals. This requires the burn-up simulation to stop at a given time and restart with a new liquid fuel composition (after removal of discarded materials and addition of fissile/fertile materials). Accounting for a continuous removal or addition is more difficult because it requires adding a term to the Bateman equations. In SCALE \cite{bowman_scale_2011}, ORIGEN \cite{gauld_isotopic_2011} solves a set of Bateman equations using spectrum-averaged fluxes and cross sections generated from a deterministic transport calculation. Methods listed in references \cite{doligez_coupled_2014,heuer_towards_2014,aufiero_extended_2013, rykhlevskii_online_2017} model true continuous feeds and removals, while other methods employ a batch-wise approach. \gls{ORNL} researchers have developed ChemTriton, a Python-based script for SCALE/TRITON which uses a semi-continuous batch process to simulate a continuous reprocessing. This tool models salt treatment, separations, discharge, and refill using a unit-cell \gls{MSR} SCALE/TRITON model over small time steps to simulate continuous reprocessing and deplete the fuel salt \cite{powers_new_2013}.

Thorium-fueled \gls{MSBR}-like reactors similar to the one in this work are described in \cite{park_whole_2015, jeong_equilibrium_2016,powers_new_2013,powers_inventory_2014, betzler_molten_2017,rykhlevskii_online_2017,nuttin_potential_2005}. Nevertheless, most of these efforts considered only simplified unit-cell geometry because depletion computations for a many-year fuel cycle are computationally expesive even for simple models.
